\newcommand{\name}{Hans Pistor}
\newcommand{\position}{Software Engineer Associate}
\newcommand{\contact}{Lockheed Martin}
\newcommand{\role}{Software Engineer Associate}
\newcommand{\email}{hpistor@fastmail.com}
\newcommand{\phone}{+1 (407) 443-5855}
\newcommand{\address}{2251 S Terrace Blvd, Longwood, Fl 32779}


\documentclass[letterpaper,11pt]{article}
\usepackage{geometry}
\usepackage{gfsdidot}

\pagenumbering{gobble}

{\setlength{\parindent}{0cm}

\geometry{
  inner=0.5in,
  top=1cm,
  bottom=1.5cm,
  right=2cm,
  left=2cm
}

\begin{document}

\begin{center}
\Large\textbf{\name} \\
\address \\
\email, \phone
\end{center}
\noindent\rule{\textwidth}{1pt}

\hfill \today

\vspace{2cm}
\textbf{Re: \position}

\vspace{0.5cm}
Dear \contact \space Team,

\vspace{0.5cm}

I hope your day is going well! My name is \name and I am very interested in working for \contact .
 Your commitment to making the world a better place by pushing technological boundaries with innovations such as SPY-7 and the Sikorsky FIREHAWK inspires me.
 The products you build and the values you stand for make \contact \space seem like an ideal workplace for me.

\vspace{0.5cm}
A little about me, I was a Jr. Applications Developer at Stetson University where I built a variety of applications for the faculty including an Android App that 
implemented 2FA using TOTP. I also contribute to various OpenSource Rust projects. I am interested in moving to a low level / embedded context and I believe
that my previous experiences as well as my ability to pick things up quickly would make me a great candidate for you.

\vspace{0.5cm}
I've attached my resume. Please let me know if there's anything else you need from me. I look forward to hearing from you!

\vspace{2cm}
Best Regards,

\vspace{0.5cm}
Hans Pistor \\
\email \\
\phone
\end{document}
